Molecular dynamics simulation of synchronization in driven particles

### 2020-11-06 manuscript/manuscript_ajp_2020.tex
updated figure captions

\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[scale=.25]{single}
\caption{\textbf{(a)} The particle is driven with a constant $F_{AC}$ and $f$ through a periodic potential landscape where blue are minima and red are maxima in the potential. \textbf{(b)} An average particle velocity in the y-direction $\bar{v}_{y}$ as a function of the driving force $F_{DC}$. In the animation the magenta dot represents the $\bar{v}_{y}$ at which the particle in Fig. 1a) is moving.}
\label{fig:1}
\end{figure}
\end{center}

@@

We simulated a twenty particle system confined to a narrow channel, as shown in Fig. 2a).  We create the confining channel with a sinusoidal function
with a single period.
\begin{equation}
  \label{eq:channel}
  V_l(x) = V_{0x} \cos{(\pi x/L)}
\end{equation}
where the trough heights is larger  $V_{0x}$,
and the associated force
\begin{equation}
\vec{F}=-\nabla V(x) = -\frac{dV}{dx} \hat{x} = - \frac{V_{0x} \pi}{L} \sin{(\pi x/L)} \hat{x}
\end{equation}
restores particles to the center of a long narrow region of the simulation.
This is shown in Fig.~\ref{fig:2}(a)
where red regions are high potential
and blue regions are low potential.

The initial configuration of the system is shown i
Fig.~\ref{fig:2}(a).  
We annealed the system into a ground-state configuration
by raising the system to a high temperature $T$,
and slowly lowering the temperature in steps of $dT=-0.01$
until the particles form a buckled chain due to the
competition between particle repulsion and channel confinement.

The interparticle forces of neighboring particles cause the system to form a buckled chain when the system is annealed.

@@

\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[scale=.40]{twenty}
\caption{\textbf{(a)} The orange particle is driven with a constant $F_{AC}$ and $f$ through 19 particles, colored green, confined by a quasi one-dimensional channel. The landscape is colored as in Fig. 1. \textbf{(b)} $\bar{v}_{y}$ versus $F_{DC}$, where $\bar{v}_{y}$ is the average particle velocity of the driven particle in the y-direction.}
\end{figure}
\end{center}

>>>>

\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[scale=.25]{single}
\caption{\textbf{(a)} The particle is driven with a constant amplitude $F_{AC}$ and frequency $\omega$ through a periodic spatial potential landscape.  The landscape is represented with a colormap where blue are minima and red are maxima in the potential. \textbf{(b)} An average particle velocity in the y-direction $\bar{v}_{y}$ as a function of a constant driving force $F_{DC}$. In the animation available in Ref.~\cite{supp1} the magenta dot represents the average velocity of the particle $\bar{v}_{y}$ at which the particle in Fig. 1(a) is moving.}
\label{fig:1}
\end{figure}
\end{center}

@@

We simulated a twenty particle system confined to a narrow channel, as shown in Fig. 2a).  We create the confining channel with a sinusoidal function
with a single period.
\begin{equation}
  \label{eq:channel}
  V_l(x) = V_{0x} \cos{(\pi x/L)}
\end{equation}
where the trough heights is larger  $V_{0x}$,
and the associated force
\begin{equation}
\vec{F}=-\nabla V(x) = -\frac{dV}{dx} \hat{x} = - \frac{V_{0x} \pi}{L} \sin{(\pi x/L)} \hat{x}
\end{equation}
restores particles to the center of a long narrow region of the simulation.
The landscape is illustrated in Fig.~\ref{fig:2}(a)
where red regions are high potential
and blue regions are low potential.

The initial configuration of the system is shown in 
Fig.~\ref{fig:2}(a).  
We annealed the system into a ground-state configuration
by raising the system to a high temperature $T$,
and slowly lowering the temperature in steps of $dT=-0.01$
until the particles form a buckled chain in the low region of the channel
due to the
competition between particle repulsion and channel confinement.
The interparticle forces between neighboring particles
cause the system to form a buckled chain. % when the system is annealed.
The molecular dynamics of simulated annealing
is described in Ref.~\ref{},
and presented simulations begin with particle configurations
that result from the annealing process,
as listed in Appendix [ref] and available in supplementary material.

@@

\begin{center}
\begin{figure}[h!]
\centering
\includegraphics[scale=.40]{twenty}
\caption{\textbf{(a)} A single particle (colored orange - mark in some manner for non-color views) is driven with a constant amplitude $F_{AC}$ and frequency $\omega$ through 19 neighboring particles (colored green - mark differently) confined by a quasi one-dimensional channel. The landscape is colored as in Fig.~\ref{fig1}(a). \textbf{(b)} Average $\bar{v}_{y}$ versus $F_{DC}$, where $\bar{v}_{y}$ is the average particle velocity of the driven particle in the y-direction.}
\label{fig:2}
\end{figure}
\end{center}
